\textit{Supplementary materials for:} Fitness tracking reveals task-specific associations between memory, mental health, and exercise

### 2021-10-20 paper/supplement.tex
(still) working on supplement figure captions

\begin{figure}[p]
\centering
\includegraphics[width=0.6\textwidth]{figs/spatial_learning_behavior}
\caption{\textbf{Spatial learning behavioral results.}}
\label{fig:spatial_behavioral}
\end{figure}

>>>>

\begin{figure}[p]
\centering
\includegraphics[width=0.6\textwidth]{figs/spatial_learning_behavior}
\caption{\textbf{Spatial learning behavioral results.}
  \textbf{a--b. Estimation error.}  Estimation
  error is defined as the Euclidean distance between each shape's
  studied and recalled positions.  The bars show the average
  estimation error (across all shapes for each memory test) versus the
  number of memorized shapes.  \textbf{a. Slope.} Estimation errors
  are broken down by the slopes of regresion lines fit to each
  participant's estimation errors as a function of the number of
  memorized shapes.  Shallower slopes (i.e., smaller decreases in
  performance associated with memorizing more shapes) are reflected by
  more saturated coloring.  Error bars denote bootstrap-estimated 95\%
  confidence intervals.  \textbf{b. Intercept.}  Bars are in the same
  format as Panel a, but here estimation errors are
  broken down by the intercepts of the same regressions used in Panel
  a.  Smaller intercepts (i.e., smaller baseline errors) are reflected
  by more saturated coloring.  \textbf{c. Distribution of slopes.}
  Across-participant distribution of regression slopes.  The lines
  denote quartile boundaries (colors are matched to Panel a).  The
  slopes are multiplied by -1 and normalized to be within the [0, 1]
  interval such that (adjusted) slopes closer to 1 reflect better
  performance and slopes closer to 0 reflect worse performance.
  \textbf{b. Distribution of intercepts.}  Across-participant
  distribution of regression intercept terms.  The lines denote
  quartile boundaries (colors are matched to Panel b).  The intercepts
  are multiplied by -1 and normalized to be within the [0, 1] interval
  such that (adjusted) intercepts closer to 1 reflect better
  performance and intercepts closer to 0 reflect worse performance.}
\label{fig:spatial_behavioral}
\end{figure}
